Study of Intra- and Inter-Job Interference with Different Job Allocations

### 2016-07-08 research_tool.tex
pass on Research Vehicle

A simulation toolkit named CODES enables the exploration of simulating different HPC networks with high fidelity \cite{Jason-2011}\cite{mubarak-sc2012}. CODES is built on top of Rensselaer Optimistic Simulation System (ROSS) parallel discrete-event simulator, which is capable of processing billions of events per second on leadership-class supercomputers \cite{ross}. CODES support both torus and dragonfly network with high fidelity flit-level simulation. CODES has this network workload component that is capable of conducting trace-driven simulations. It can take real MPI application traces generated by SST DUMPI \cite{sst} to drive CODES network models. In this work, we focus on an in-depth analysis of intra- and inter-job communication interferences with  different job allocations on torus-connected HPC systems. Torus networks have been extensively used in the current generation of supercomputers because of their linear scaling on per-node cost and competitive communication performance \cite{mubarak-sc2012}\cite{zhou-ipdps}.

>>>>

A simulation toolkit named CODES enables the exploration of simulating 
different HPC networks at flit-level with high fidelity~\cite{Jason-2011, mubarak-sc2012}. 
CODES is built on top of Rensselaer Optimistic Simulation System (ROSS) parallel discrete-event simulator~\cite{ross}, 
which is capable of processing billions of events per second on leadership-class supercomputers. 
CODES support both torus and dragonfly network with high fidelity flit-level simulation. 
CODES has this network workload component that is capable of conducting trace-driven simulations. 
It can take MPI application traces generated by SST DUMPI \cite{sst} to drive CODES network models. 
In this work, we focus on an in-depth analysis of intra- and inter-job 
communication interferences with different job allocations on torus-connected HPC systems. 
Torus networks have been extensively used in the current generation of supercomputers 
because of their linear scaling on per-node cost and competitive communication performance.
